\section{Introduction}

Some model failures are hard to explain. Others are instantly legible: the
model counts the wrong number of letters, removes the wrong character, ignores
an output format, or answers a prompt whose key constraint was written in plain
view. These are small failure modes, but they matter because users can
recognize them immediately.

\benchmarkname{} focuses on that surface. It is not intended to replace broad
capability benchmarks. It asks a narrower question: can a model reliably handle
short, objective, single-turn prompts that look obvious to a careful human and
are easy to score without an LLM judge?

The benchmark is intentionally simple. Items are short. Answers are objective.
Scorers are deterministic. The report shows answer accuracy, format accuracy,
strict accuracy, and cost rather than a single undifferentiated score. The
headline score is answer correctness; strict accuracy remains visible as an
interface-compliance diagnostic. The goal is to make obvious failures easy to
track, compare, and regress.

The intended contributions are:

\begin{itemize}
  \item a 224-question \paperSplit{} manifest spanning eight obvious-task
        families;
  \item reviewed item cards with source summaries, answer derivations,
        ambiguity notes, scorer contracts, and split-policy rationale;
  \item deterministic scoring that separates answer correctness from format
        compliance; and
  \item a frozen 2026-06-03 evidence snapshot covering 223 model settings,
        178 unique model identifiers, provider outcomes, cost, and token burden.
\end{itemize}
