\section{Analysis}

The following patterns are descriptive slices of the evidence run. They should
be treated as hypotheses about where obvious-task brittleness appears, not as
claims about hidden model mechanisms.

\paragraph{Answer versus format failures.}
Answer correctness and strict accuracy diverge when a model solves the task but
misses the requested interface. This matters for models that append
explanations, change capitalization in a tolerated answer, or return a
JSON-like value that is semantically right but not strictly formatted. For that
reason, answer correctness is the primary score and strict correctness remains
a secondary compliance diagnostic.

\paragraph{Family hotspots.}
The hardest aggregate families in this run are character counting and spelling
transforms. Across model-family rows, character counting reaches about 61\%
answer correctness and spelling transforms about 65\%, while format
compliance, word counting, negation, and ordering are all above 95\% aggregate
answer correctness. The wrong-answer review shows the same shape: the most
common failure tags are incorrect counts, wrong letter or substring edits, and
verbose noncompliance.

\paragraph{Metamorphic instability.}
Paired variants can show whether a model handles similar obvious operations
consistently. The current paper keeps these checks exploratory: a model that
passes one spelling or counting variant and fails a nearby variant is a useful
debugging target, but the first draft does not promote paired deltas above the
main answer-correctness result.

\paragraph{Thinking, defaults, and cost.}
The report separates configured thinking settings from reported reasoning-token
telemetry. A row with nonzero reported reasoning tokens is not automatically a
known discrete thinking-level run. Where explicit settings exist, higher effort
often improves accuracy, but the token and cost burden can rise sharply for
tasks whose answers are short. The paper therefore reads accuracy, cost per
correct answer, and tokens per correct answer together.

\begin{table}[H]
  \centering
  \caption{Sample-weighted grouping by configured or inferred thinking mode.
  Reported reasoning tokens are telemetry and should not be interpreted as a
  requested thinking level unless the run metadata explicitly says so.}
  \label{tab:thinking-group-results}
  \input{tables/thinking_group_results}
\end{table}

\begin{table}[H]
  \centering
  \caption{Sample-weighted grouping by broad model family. This table separates
  provider/family-level patterns from individual model-setting rows.}
  \label{tab:model-family-results}
  \input{tables/model_family_results}
\end{table}

\begin{table}[H]
  \centering
  \caption{Most common failure types in the wrong-answer review. Counts include
  answer-wrong rows and format-only review rows.}
  \label{tab:failure-type-summary}
  \input{tables/failure_type_summary}
\end{table}
