\section{Limitations, Ethics, and Reproducibility}

\paragraph{Limitations.}
\benchmarkname{} is narrow. It does not measure general intelligence,
truthfulness, safety, retrieval, tool use, long-context behavior, or multi-turn
agent performance. Public examples are contamination-prone. Generated variants
can be flawed. Deterministic scorers can be too strict or too permissive.
Model aliases, provider behavior, and pricing can change.

The evidence run includes both direct-provider models and OpenRouter-routed
models, and the full appendix/report may include special-purpose or
non-general-chat rows. Main-text rankings should therefore be read as a
measurement snapshot under recorded routing and pricing assumptions, not as a
stable market-wide ranking. Free endpoints, promotional routes, and manually
patched prices require a pricing vintage before cost claims are reused.

\paragraph{Ethics and source safety.}
The benchmark should not republish private information, private account data,
screenshots without permission, raw provider headers, credentials, or private
prompts. Public examples should be treated as source leads, and generated
variants should avoid naming private individuals.

\paragraph{AI tool assistance.}
AI coding and writing-assistance tools were used during code development,
artifact generation, literature triage, drafting, editing, and consistency
checks. The author reviewed the manuscript and release artifacts and takes
responsibility for all content, analyses, citations, and claims.

\paragraph{Reproducibility.}
The final paper should release the code, paper split manifest, public item
cards, scorer-gold fixtures, model run manifest, generated tables, generated
figures, and exact commands. It should state the git commit, data vintage,
pricing vintage, model aliases, run dates, and exclusion policy for provider
errors. If provider errors, refusals, or timeouts remain after configured
retries, they should be counted as incorrect final attempts and separately
reported as provider diagnostics.

\begin{table}[t]
  \centering
  \caption{Current paper-readiness gates.}
  \label{tab:readiness-gates}
  \input{tables/readiness_gates}
\end{table}
